\chapter{Conclusion and Future Work}
Basically, all the procedure of detecting eating and talking from video recorded by webcam are finished. The difficulty of processing data is that the data usually is very diverse and there is no standard procedure, for different situation, different methodologies are used. For example, as there are many head movement in the videos, removing head pose from feature data seems to be very important. Data is vital to machine learning, basically data and model would directly decide the results. In this project, the importance of data and model are never should be underestimated. The result of classification is very unsatisfying. There are several reasons that would lead to this result. The process of remove head pose from shape feature vector, the transformation is not perfect, it will lose and change some information of shape feature. Secondly, the videos should be more carefully filtered, as videos are very diverse. Resolution, recording environment, lighting condition are different for each video. The most important and difficult problem may be remove head pose from face image and transform appearance image and facial feature points to frontal face. Thirdly, Support Vector Machine(SVM) may not very good at for this project. Since eating and talking contain state changing, using each frame as entity may not be a good idea. However, the number of frames in each videos is very different. A sequence may contains many section of eating, the video should be manually segmented if use SVM to train by sequences. In addition, frame number of each sequence is different, basically it is impossible to try to train an SVM using sequences.

As the time is restricted, we just carried on the experiment using SVM. There are much more selection for classification model, such as Hidden Markov Model, Long-short term memory neural network. There are many more other method could be tried, such as tracker for facial feature tracking, methodology of de-composite facial feature point and remove head pose, methodology of transform appearance image and facial feature points, extract different features. What's more, the video data could be categorised better and more filter and organisation could be done.

